---
title: "Quant demo for company B3"
author: "Sabrina Norwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    toc: yes
    toc_float: yes
---

# Research Questions

- How satisfied are people with the service?
- If you want to improve overall satisfaction, what elements of the service would you focus on?
- If you want to minimize dissatisfaction, where needs attention?

```{r include=FALSE}

# options
## turn off scientific notation
options(scipen=999)

## chunk options
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)


# dependencies

library(tidyverse)
library(readxl)
#library(strengejacke)  # library(devtools); install_github("strengejacke/strengejacke")
library(sjPlot)  # library(devtools); install_github("strengejacke/sjPlot")
# library(knitr)
# library(kableExtra)
# library(psych)
library(janitor)
library(lemon)

# get data
data_cleaned <- read_xlsx("../data/raw/Use case datafile.xlsx") %>%
  clean_names()
  
```

# Descriptives

```{r}

data_summary_temp <- data_cleaned %>%
  # "gather" a bunch of items into fewer columns
  gather(item, response, c(overall_recommendation_score, website_score, brochures_score, call_center_score, personal_advisor_score, project_coordinator_score, technician_installer_score, timing_score, product_score, after_sales_service_score)) %>%
  group_by(item) %>% # for each item...
  count(response) %>% # ...create counts
  mutate(percent = round(n/sum(n)*100, 0)) %>% # convert counts to percents, rounding to zero decimals
  mutate(item = str_replace_all(item, "_", " "), 
         item = str_remove(item, " score"),
         item = str_to_title(item))

```

```{r fig.height=5, fig.width=6}

p1 <- data_summary_temp %>%
  filter(item != "Overall Recommendation") %>%
  ggplot(aes(response, percent, fill = response)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item) + # scales = "free_y" 
  #lemon::facet_rep_wrap(~ item, repeat.tick.labels = "x") +
  scale_fill_viridis_c(begin = 0.3, end = 0.7) +
  #geom_vline(aes(xintercept = 5.5), linetype = "dashed")
  ylab("Percent") +
  xlab("Score") + 
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10)) +  # how to label the axis ticks
  # scale_x_continuous(breaks = c(1, 5, 9),
  #                    labels = c("Unsatisfied", "Neutral", "Satisfied")) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none")

p1

ggsave(filename = "p1.pdf", 
       plot = p1, 
       device = "pdf",
       height = 5,
       width = 7,
       units = "in")

```

```{r fig.height=4, fig.width=5}

p2 <- data_summary_temp %>%
  filter(item == "Overall Recommendation") %>%
  ggplot(aes(response, percent, fill = response)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item) + # scales = "free_y" 
  scale_fill_viridis_c(begin = 0.3, end = 0.7) +
  #geom_vline(aes(xintercept = 5.5), linetype = "dashed")
  ylab("Percent") +
  xlab("Score") + 
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10)) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none")

p2

ggsave(filename = "p2.pdf", 
       plot = p2, 
       device = "pdf",
       height = 3,
       width = 4,
       units = "in")

```

# Regression

## multivariable - inappripriate and returns nonsense conclusions

(included only to demonstrate this point)

```{r}

fit_1 <- lm(overall_recommendation_score ~ website_score + brochures_score + call_center_score + personal_advisor_score + project_coordinator_score + technician_installer_score + timing_score + product_score + after_sales_service_score, 
            data = data_cleaned)

plot_model(fit_1)

```

## multiple regression models

which variables were collected in what order?

### linear

```{r}

data_reshaped <- data_cleaned %>%
  gather(predictor, response, c(website_score, brochures_score, call_center_score, personal_advisor_score, project_coordinator_score, technician_installer_score, timing_score, product_score, after_sales_service_score)) 

results_linear <- data_reshaped %>%
  group_by(predictor) %>%
  #group_map(~ broom::tidy(lm(overall_recommendation_score ~ response, data = .x)))
  do(broom::tidy(lm(overall_recommendation_score ~ response, data = .))) %>%
  # for this analysis (but not all!) we discard the intercept
  filter(term == "response") %>%
  # calculate confidence intervals
  mutate(ci_lower = estimate - std.error*1.96,
         ci_upper = estimate + std.error*1.96,
         sig = ifelse(p.value < .01, "sig", "nonsig"))

# ggplot(results_linear, aes(forcats::fct_reorder(predictor, estimate), estimate, fill = sig)) +
#   geom_bar(stat = "identity") +
#   #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   coord_flip() +
#   scale_fill_viridis_d(begin = 0.3, end = 0.7)

p5 <- ggplot(results_linear, aes(forcats::fct_reorder(predictor, estimate), estimate, fill = estimate)) +
  geom_bar(stat = "identity") +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  coord_flip() +
  scale_fill_viridis_c(begin = 0.3, end = 0.7) +
  ylab("Expected impact on\nOverall Recommendation score") +
  xlab("") +
  scale_x_discrete(
    labels = 
      results_linear %>%
      arrange(estimate) %>%
      pull(predictor) %>%
      str_replace_all("_", " ") %>%
      str_remove(" score") %>%
      str_to_title()
  ) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none")

p5

ggsave(filename = "p5.pdf", 
       plot = p5, 
       device = "pdf",
       height = 5,
       width = 7,
       units = "in")

# ggplot(results_linear, aes(forcats::fct_reorder(predictor, estimate), estimate, color = sig)) +
#   geom_point() +
#   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   geom_hline(aes(yintercept = 0), linetype = "dashed") +
#   coord_flip() +
#   scale_color_viridis_d(begin = 0.3, end = 0.7)
# 
# results_linear %>%
#   arrange(desc(estimate)) %>%
#   select(predictor, estimate)

```

### ranks

Linear regression might not be robust given skew. Do a robustness test too.

```{r}

results_rank <- data_reshaped %>%
  group_by(predictor) %>%
  mutate(overall_recommendation_score = rank(overall_recommendation_score),
         response = rank(response)) %>%
  #group_map(~ broom::tidy(lm(overall_recommendation_score ~ response, data = .x)))
  do(broom::tidy(lm(overall_recommendation_score ~ response, data = .))) %>%
  # for this analysis (but not all!) we discard the intercept
  filter(term == "response") %>%
  # calculate confidence intervals
  mutate(ci_lower = estimate - std.error*1.96,
         ci_upper = estimate + std.error*1.96,
         sig = ifelse(p.value < .005, "sig", "nonsig"))

ggplot(results_rank, aes(forcats::fct_reorder(predictor, estimate), estimate, fill = estimate)) +
  geom_bar(stat = "identity") +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  coord_flip() +
  scale_fill_viridis_c(begin = 0.3, end = 0.7) +
  ylab("Expected impact on\nOverall Recommendation\n(ranked customers)") +
  xlab("") +
  scale_x_discrete(
    labels = 
      results_rank %>%
      arrange(estimate) %>%
      pull(predictor) %>%
      str_replace_all("_", " ") %>%
      str_remove(" score") %>%
      str_to_title()
  ) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") 

# ggplot(results_rank, aes(forcats::fct_reorder(predictor, estimate), estimate, color = sig)) +
#   geom_point() +
#   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   geom_hline(aes(yintercept = 0), linetype = "dashed") +
#   coord_flip() +
#   scale_color_viridis_d(begin = 0.3, end = 0.7)

```

## Compare methods

```{r}

bind_rows(mutate(results_linear, method = "linear"), 
          mutate(results_rank, method = "rank")) %>%
  ggplot(aes(forcats::fct_reorder(predictor, estimate), estimate, fill = estimate, group = method)) +
  geom_bar(stat = "identity", position = position_dodge(width = .9)) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  coord_flip() +
  scale_fill_viridis_c(begin = 0.3, end = 0.7)

```

```{r}

p3 <- data_reshaped %>%
  mutate(predictor = str_replace_all(predictor, "_", " "),
         predictor = str_remove(predictor, " score"),
         predictor = str_to_title(predictor),
         highlight = ifelse(response >= 5 | is.na(response), "normal", "highlight")) %>%
  ggplot(aes(response, overall_recommendation_score)) +
  ylab("Overall Recommendation") +
  xlab("Response") +
  theme(legend.position = "none") +
  geom_jitter(aes(color = highlight), alpha = 0.5) +
  scale_color_manual(values = c("highlight" = "#440154", "normal" = "#44bf70")) +
  geom_smooth(method = "lm", se = FALSE, colour = "darkgrey", size = 0.75) +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) +
  coord_cartesian(xlim = c(-0.5, 10.5), ylim = c(-0.5, 10.5)) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none") +
  facet_wrap(~ predictor)
  #lemon::facet_rep_wrap(~ predictor, repeat.tick.labels = TRUE)

p3

ggsave(filename = "p3.pdf", 
       plot = p3, 
       device = "pdf",
       height = 7,
       width = 7,
       units = "in")

```

```{r}

data_reshaped_negative_experience <- data_reshaped %>%
  mutate(negative_experience = ifelse(response <= 5, TRUE, FALSE)) %>%
  group_by(predictor) %>%
  summarize(percent_negative_experience = sum(negative_experience, na.rm = TRUE)/n())

p4 <- ggplot(data_reshaped_negative_experience, aes(forcats::fct_reorder(predictor, percent_negative_experience), percent_negative_experience, fill = percent_negative_experience)) +
  geom_bar(stat = "identity") +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  coord_flip() +
  scale_fill_viridis_c(begin = 0.3, end = 0.7, direction = -1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  ylab("Customers with a\nneutral or negative experience") +
  xlab("") +
  scale_x_discrete(
    labels = 
      data_reshaped_negative_experience %>%
      arrange(percent_negative_experience) %>%
      pull(predictor) %>%
      str_replace_all("_", " ") %>%
      str_remove(" score") %>%
      str_to_title()
  ) +
  theme_bw() +
  theme(strip.background = element_blank()) +
  theme(legend.position = "none")

p4

ggsave(filename = "p4.pdf", 
       plot = p4, 
       device = "pdf",
       height = 5,
       width = 7,
       units = "in")

```

```{r}

data_reshaped_type_experience <- data_reshaped %>%
  mutate(type_experience = case_when(response < 5 ~ "Negative", 
                                     response == 5 ~ "Neutral", 
                                     response > 5 ~ "Positive")) %>%
  count(predictor, type_experience) %>%
  drop_na() %>%
  group_by(predictor) %>%
  mutate(percent = n/sum(n))

ggplot(data_reshaped_type_experience, aes(predictor, percent, fill = type_experience)) +
  geom_bar(position = "stack", stat = "identity") +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  coord_flip() +
  scale_fill_viridis_d(begin = 0.3, end = 0.7, direction = -1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  #ylab("Customers with a\nnegative experience") +
  # xlab("") +
  # scale_x_discrete(
  #   labels = 
  #     data_reshaped_negative_experience %>%
  #     arrange(percent_negative_experience) %>%
  #     pull(predictor) %>%
  #     str_replace_all("_", " ") %>%
  #     str_remove(" score") %>%
  #     str_to_title()
  # ) +
  theme_bw() +
  theme(strip.background = element_blank()) 
  #theme(legend.position = "none")

```

```{r}

data_reshaped_type_experience <- data_reshaped %>%
  count(predictor, response) %>%
  drop_na() %>%
  group_by(predictor) %>%
  mutate(percent = n/sum(n))

ggplot(data_reshaped_type_experience, aes(predictor, percent, fill = response)) +
  geom_bar(position = "stack", stat = "identity") +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  coord_flip() +
  scale_fill_viridis_c(begin = 0.1, end = 0.9, option = "magma") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  #ylab("Customers with a\nnegative experience") +
  # xlab("") +
  # scale_x_discrete(
  #   labels = 
  #     data_reshaped_negative_experience %>%
  #     arrange(percent_negative_experience) %>%
  #     pull(predictor) %>%
  #     str_replace_all("_", " ") %>%
  #     str_remove(" score") %>%
  #     str_to_title()
  # ) +
  theme_bw() +
  theme(strip.background = element_blank()) 
  #theme(legend.position = "none")

```

## correlations

```{r}

correlation_results <- data_cleaned %>%
  select(-respondent_id) %>%
  cor(use = "pairwise.complete.obs") %>%
  round(2) %>%
  as.data.frame() %>%
  rownames_to_column(var = "predictor") %>%
  filter(predictor != "overall_recommendation_score") %>%
  select(predictor, correlation = overall_recommendation_score) %>%
  arrange(desc(correlation)) 

correlation_results

```





